---
title: "EAAFP interactive map development page"
author: "YCChan"
date: "9/15/2020"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

---
This site is for development purpose.

Counts of > 0.25% of the EAAF population size estimate of a species is displayed.

Template for submitting your count data can be downloaded [here.](https://github.com/chanyingchi/EAAFPmap.develop/raw/master/count.data.submit.template.xlsx)


Here you can see the maps containing the data we have collected so far. After we have received your data, We will update it as soon as we can!

***
## Bar-tailed Godwit distribution map

```{r include=FALSE}
source('C:/Users/chan/work/Company/EAAFP species dist map/EAAFP map app/server.R')
datapath<-('C:/Users/chan/work/Company/EAAFP species dist map/species dist data/')
 d.in<-
      read_excel(paste(datapath,'d.btg.all.input.xlsx',sep=''),col_types=c(rep( "guess",3),'text',rep( "guess",8)))
    d.in$subsp[d.in$subsp=='NA']<-NA
    circle.size=5
    d.in$circle.size<-(1.5+circle.size/10)+(log10(1+(d.in$max.count/min(d.in$max.count))*5)*(1+circle.size/8))
m<-make.map(d.in)

```

```{r echo=FALSE, fig.height = 7}
m
```


Bar-tailed Godwit data:
Flyway population estimate: 279,000

```{r echo=FALSE,layout="l-body-outset"}
library(DT)
d.in<-d.in[order(d.in$lat),]
datatable(d.in[,c(1:4,8:12)])
```


***

## Far Eastern curlew distribution map:

```{r include=FALSE}
source('C:/Users/chan/work/Company/EAAFP species dist map/EAAFP map app/server.R')
datapath<-('C:/Users/chan/work/Company/EAAFP species dist map/species dist data/')
 d.fec<-
      read_excel(paste(datapath,'d.fec.all.input.xlsx',sep=''),col_types=c(rep( "guess",3),'text',rep( "guess",8)))
 d.in<-d.fec
    d.in$subsp[d.in$subsp=='NA']<-NA
    circle.size=5
    d.in$circle.size<-(1.5+circle.size/10)+(log10(1+(d.in$max.count/min(d.in$max.count))*5)*(1+circle.size/8))
m<-make.map(d.in)

```

```{r echo=FALSE, fig.height = 7}
m
```

Far Eastern Curlew data:
Flyway population estimate: 32,000
```{r echo=FALSE,layout="l-body-outset"}
library(DT)
d.fec<-d.fec[order(d.fec$lat),]
datatable(d.fec[,c(1:4,8:12)])
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
Data sources:
Andreas Kim
Conklin, J. R., Verkuil, Y.	I., & Smith, B. R. (2014).	Prioritizing migratory shorebirds for conservation: Action on the East Asian-Australasian flyway. WWF‐Hong Kong.
Jaensch, R. (2013). New tools for development of the flyway site network: An integrated and updated list of candidate sites and guidance on prioritisation. Report to Partnership for the East Asian–Australasian Flyway. 
Chan, Y. C., Peng, H. B., Han, Y. X., Chung, S. S. W., Li, J., Zhang, L., & Piersma, T. (2019). Conserving unprotected important coastal habitats in the Yellow Sea: shorebird occurrence, distribution and food resources at Lianyungang. Global Ecology and Conservation, 20, e00724.
