---
title: "EAAFP interactive map development page"
author: "YCChan"
date: "4/12/2020"
output: html_document

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

---
This site is for development purpose.

Counts of > 0.25% of the EAAF population size estimate of a species is displayed.

Template for submitting your count data can be downloaded [here.](https://github.com/chanyingchi/EAAFPmap.develop/raw/master/count.data.submit.template.xlsx)


Here you can see the maps containing the data we received so far. After we have received your data, We will update it as soon as we can!

***

## Black-faced Spoonbill distribution map

```{r include=FALSE}
library(DT)
source('C:/Users/chan/work/Company/EAAFP species dist map/EAAFP map app/server.R')
datapath<-('C:/Users/chan/work/Company/EAAFP species dist map/species dist data/')
 d.bfs<-
      read_excel(paste(datapath,'d.bfs.xlsx',sep=''),col_types=c(rep( "guess",3),'text',rep( "guess",8)))
 d.in<-d.bfs
    d.in$subsp[d.in$subsp=='NA']<-NA
    circle.size=5
    d.in$circle.size<-(1.5+circle.size/10)+(log10(1+(d.in$max.count/min(d.in$max.count))*5)*(1+circle.size/8))
m<-make.map(d.in)

```

```{r echo=FALSE, fig.height = 7}
m
```
Note: Non-breeding sites with a population >0.25% in at least 5 years within the period of 2011-2020 are included in this map. An exception is Xuanmun Bay of Zhejiang Province, where large numbers of Black-faced Spoonbill were counted in recent years.


Black-faced Spoonbill data:

```{r echo=FALSE, layout="l-body-outset"}

d.bfs<-d.bfs[order(d.bfs$lat),]
datatable(d.bfs[,c(1:4,8:12)])
```
***

Data sources:

Hong Kong Bird Watching Society. International BFS Census Report 2011-2020 (data compiled by Yu Yat-Tung)

Choi, et.al. 2020. China Coastal Waterbird Census Report  (Jan. 2012 - Dec. 2019). Hong Kong: Hong Kong Bird Watching Society

Chong, JR. 2014. A Survey of Black-faced Spoonbill <i>Platalea minor</i> in the Korean Yellow Sea, summer 2012. Hong Kong Bird Report 2012. pp: 308-322. Hong Kong Bird Watching Society. Hong Kong.

Kang J-H, Kim I K, Lee K-S, Lee H & Rhim S-J (2016) Distribution, breeding status, and conservation of the black-faced spoonbill (Platalea minor) in South Korea, Forest Science and Technology, 12:3, 162-166, DOI:
10.1080/21580103.2015.1090483

***

## Bar-tailed Godwit distribution map

```{r include=FALSE}
library(DT)
source('C:/Users/chan/work/Company/EAAFP species dist map/EAAFP map app/server.R')
datapath<-('C:/Users/chan/work/Company/EAAFP species dist map/species dist data/')
 d.in<-
      read_excel(paste(datapath,'d.btg.all.input.inc.new.data.xlsx',sep=''),col_types=c(rep( "guess",3),'text',rep( "guess",8)))
 d.in$max.count<-as.numeric(d.in$max.count)
    d.in$subsp[d.in$subsp=='NA']<-NA
    circle.size=5
    d.in$circle.size<-(1.5+circle.size/10)+(log10(1+(d.in$max.count/min(d.in$max.count))*5)*(1+circle.size/8))
m<-make.map(d.in)

```

```{r echo=FALSE, fig.height = 7}
m
```


Bar-tailed Godwit data:

Flyway population estimate: 279,000

```{r echo=FALSE, layout="l-body-outset"}

d.in<-d.in[order(d.in$lat),]
d.in$lat<-round(as.numeric(d.in$lat),3)
d.in$lon<-round(as.numeric(d.in$lon),3)
datatable(d.in[,c(1:4,8:12)])
```


***

## Far Eastern curlew distribution map:

```{r include=FALSE}
source('C:/Users/chan/work/Company/EAAFP species dist map/EAAFP map app/server.R')
datapath<-('C:/Users/chan/work/Company/EAAFP species dist map/species dist data/')
 d.fec<-
      read_excel(paste(datapath,'d.fec.all.input.inc.new.data.xlsx',sep=''),col_types=c(rep( "guess",3),'text',rep( "guess",8)))
 d.in<-d.fec
 d.in$max.count<-as.numeric(d.in$max.count)
    d.in$subsp[d.in$subsp=='NA']<-NA
    circle.size=5
    d.in$circle.size<-(1.5+circle.size/10)+(log10(1+(d.in$max.count/min(d.in$max.count))*5)*(1+circle.size/8))
m<-make.map(d.in)

```

```{r echo=FALSE, fig.height = 7}
m
```

Far Eastern Curlew data:

Flyway population estimate: 32,000
```{r echo=FALSE,layout="l-body-outset"}
library(DT)
d.fec<-d.fec[order(d.fec$lat),]
d.fec$lat<-round(as.numeric(d.fec$lat),3)
d.fec$lon<-round(as.numeric(d.fec$lon),3)
datatable(d.fec[,c(1:4,8:12)])
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
Data sources:
<br>
Chan, Y. C., Peng, H. B., Han, Y. X., Chung, S. S. W., Li, J., Zhang, L., & Piersma, T. (2019). Conserving unprotected important coastal habitats in the Yellow Sea: shorebird occurrence, distribution and food resources at Lianyungang. Global Ecology and Conservation, 20, e00724.
<br>

Conklin, J. R., Verkuil, Y.	I., & Smith, B. R. (2014).	Prioritizing migratory shorebirds for conservation: Action on the East Asian-Australasian flyway. WWF‐Hong Kong.
<br>

Jaensch, R. (2013). New tools for development of the flyway site network: An integrated and updated list of candidate sites and guidance on prioritisation. Report to Partnership for the East Asian–Australasian Flyway.
<br>

Korean Shorebird Network 2011-2015. Shorebird Monitoring Report of Korea. (data compiled by Andreas Kim)
<br>

MYSMA database: Rogers, D.I., Scroggie, M.P. and Hassell, C.J. 2020. Review of long-term shorebird monitoring in north western Australia. Arthur Rylah Institute for Environmental Research Technical Report Series No. 313.
<br>

Ornithological Society of New Zealand. Wader Census database.
<br>

Ruthrauff, D. R., Pohlen, Z. M. and Wilson, H. M., 2020, Aerial surveys of shorebirds at pre-migratory staging sites in western Alaska, 2018-2019: U.S. Geological Survey data release, https://doi.org/10.5066/P9ZS5Y6N.
<br>

Unpublished data of National Institute for Biological Resources, South Korea.
<br>
